Your Paper Title

### 2025-03-26 paper/paper.qmd
corrected author name from Chris Du to Chris Lu in paper files

---
title: "Your Paper Title"
subtitle: "So fancy!"
author:
    - Luca Carnegie
    - Chris Du
    - Russell Luchin
    - Randall Ni
abstract:
    This is the abstract of your paper. Write a brief summary of your research,
    including your objectives, methods, key results, and main conclusions.
    Keep it concise but informative.
keywords: [keyword1, keyword2, keyword3]
format:
    pdf:
        documentclass: article
        papersize: letter
        toc: true
        number-sections: true
        colorlinks: true
        fig-cap-location: bottom
        tbl-cap-location: top
        geometry: "margin=1in"  
bibliography: references.bib
execute:
    echo: false  # Hide code by default
    warning: false
    message: false
    jupyter: "python"
---

>>>>

---
title: "Your Paper Title"
subtitle: "So fancy!"
author:
    - Luca Carnegie
    - Chris Lu
    - Russell Luchin
    - Randall Ni
abstract:
    This is the abstract of your paper. Write a brief summary of your research,
    including your objectives, methods, key results, and main conclusions.
    Keep it concise but informative.
keywords: [keyword1, keyword2, keyword3]
format:
    pdf:
        documentclass: article
        papersize: letter
        toc: true
        number-sections: true
        colorlinks: true
        fig-cap-location: bottom
        tbl-cap-location: top
        geometry: "margin=1in"  
bibliography: references.bib
execute:
    echo: false  # Hide code by default
    warning: false
    message: false
    jupyter: "python"
---
